Untitled

### 2017-06-13 EmptyHomesV1.Rmd
Function Update
Updated functions including new ones to make leaflet plotting easier. These were the last changes before publishing the chelsea blog

@@

@@

@@

>>>>

Chelseainfo2 <- read_excel( "Kensington and ChelseaDiscountsLSOA.xlsx" )[,1:4] %>%
  StructureData(full= FALSE)
colSums(Chelseainfo2[,-1])

@@

sum(Chelseainfo$LowUse)/sum(Chelseainfo$Homes)

@@

ChelseainfoWard <- Chelseainfo %>% 
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first))

@@

ChelseaWardHomesStrap2 <- ClassStrapper(ChelPrice, sum(ChelseainfoWard$WardHomes), 10000)

### 2017-06-13 PlotwithLeaflet.Rmd
Chelsea Analysis
Added some code which performs an analysis for Chelsea.
Function Update
Updated functions including new ones to make leaflet plotting easier. These were the last changes before publishing the chelsea blog

---
title: "Untitled"
author: "Jonathan Bourne"
date: "29 May 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

@@

setwd("/home/jonno")
list.files()

states <- geojsonio::geojson_read("us-states.geojson" , what = "sp")
class(states)

@@

m <- leaflet(states) %>%
  #setView(-96, 37.8, 4) %>%
  addTiles()
  # addProviderTiles("MapBox", options = providerTileOptions(
  #   id = "mapbox.light",
  #   accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))

m %>% addPolygons()

@@

```{r}
MyData <- AG %>% filter(grepl("kensington", LAD11NM ,ignore.case = T)) %>%
  rename(LSOA_CODE = lsoa11cd)

MyData <- SpatialPointsDataFrame(coords =MyData[,c(1,2)], data = MyData,
                               proj4string = CRS('+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +datum=OSGB36 +units=m +no_defs'))
MyData <- spTransform(MyData, CRS("+init=epsg:4326"))
#random thing
stuff <-data.frame(LSOA_CODE=unique(MyData$LSOA_CODE),row.names=unique(MyData$id))

MyData<- points2polygons(MyData,stuff)

#AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))

MyData <- Chelseainfo %>%
  select(LSOA_CODE, LowUsePerc, WD16NM)%>%
  merge(MyData, .)

class(MyData) # data.frame

v<-"pk.eyJ1Ijoiam9ubm9iIiwiYSI6ImNqM2FlNXhpbDAwM3gzMW83ZW1hbHI0bzYifQ.4AfaY0Un0bKU41hZscpy9Q"

m <- leaflet(MyData) %>%
    #addTiles()
    addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = v))

bins <- c(0, 10, 20, 25, 100)
pal <- colorBin("YlOrRd", domain = MyData$LowUsePerc, bins = bins)

labels <- sprintf(
  "<strong>%s</strong><br/>Low-use  %g &#37",
  MyData$WD16NM, MyData$LowUsePerc
) %>% lapply(htmltools::HTML)

z <-m %>% addPolygons(
  fillColor = ~pal(LowUsePerc),
  weight = 2,
  opacity = 1,
  color = "white",
  dashArray = "3",
  fillOpacity = 0.7,
  highlight = highlightOptions(
    weight = 5,
    color = "#666",
    dashArray = "",
    fillOpacity = 0.7,
    bringToFront = TRUE),
  label = labels,
  labelOptions = labelOptions(
    style = list("font-weight" = "normal", padding = "3px 8px"),
    textsize = "15px",
    direction = "auto")) %>%
  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
    position = "bottomright")

#saveWidget(z, file="m.html", selfcontained = FALSE )
setwd("/home/jonno")
mapshot(z, url = paste0(getwd(), "/map.html"))
```

>>>>

---
title: "Untitled"
author: "Jonathan Bourne
date: "29 May 2017"
output: html_document
---

```{r}

library(htmlwidgets)
gitpage <- "/home/jonno/JonnoB.github.io"

@@

@@

@@

```{r}
setwd(gitpage)
z <- MakeLeaflet("chelsea", Chelseainfo)
z
saveWidget(z, file="ChelseaLowUse.html", selfcontained = TRUE )

z<- MakeLeaflet("lambeth", Lambethinfo, c(0:5))
saveWidget(z, file="LambethLowUSe.html", selfcontained = TRUE )

setwd("/home/jonno")
mapshot(z, url = paste0(getwd(), "/map.html"))
```
